---
title: "Alcohol vs Seat choice"
author: "Dominic Garibay"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.  

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(mydata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

``` {r include = TRUE, echo = FALSE}
ggplot(data = mydata, aes(x = Seat, y = alcohol) ) +
geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
stat_boxplot (geom ='errorbar') +
labs (x = "alcohol", y = "Seat", title = "Alcohol consumed by seating") +
theme (plot.title = element_text(hjust = 0.5, size = 16) )
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=FALSE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

``` {r include = TRUE, echo = FALSE}
favstats(alcohol~Seat,data=mydata)
```



## Inferential Tests

``` {r include = TRUE, echo = FALSE}
model1 <- aov(alcohol~Seat,data=mydata)
summary.aov(model1)
```


## Conclusions


