---
title: "Alcohol vs Seat choice"
author: "Dominic Garibay"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
mydata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.  

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(mydata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

``` {r include = TRUE, echo = FALSE}
ggplot(data = mydata, aes(x = Seat, y = alcohol) ) +
geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
stat_boxplot (geom ='errorbar') +
labs (x = "alcohol", y = "Seat", title = "Alcohol consumed by seating") +
theme (plot.title = element_text(hjust = 0.5, size = 16) )
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=FALSE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

``` {r include = TRUE, echo = FALSE}
favstats(alcohol~Seat,data=mydata)
```

The favstats data shows that the mean alcohol consumption is significantly higher in the Back row group when compared to the Front and Middle rows. The Middle row has an alcohol consumption closer to the Front row with a median of about 3.3 but, the Front row has the mean of the lowest alcohol consumption of about 1.8. The arrangements of the seating and their correlation to alcohol consumption is consistent across the mean and the median as the median arranged from least to greatest amount of alcohol consumption is Front(0), Middle(1), and Back(4).

## Inferential Tests

``` {r include = TRUE, echo = FALSE}
model1 <- aov(alcohol~Seat,data=mydata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1,conf.level = 0.95))
```

The TukeyHSD  test shows that the there is a significant difference between the middle and back seats with alcohol level and a significant difference between the front and back row with alcohol level. There is not a significant difference between the middle and front rows with alcohol level as the test is run with a 99% confidence interval.


## Conclusions

Looking at the data and analyzing it through numerical summaries and the box plots allow us to see the difference in alcohol consumption between the different seating rows. It was found that there was a significant difference in alcohol consumption when comparing the middle-back rows and the front-back rows. This confirms the alternate hypothesis that the average number of drinks is different between two rows as confirmed by the TukeyHSD plot with a 99% confidence interval.
